### 2019-10-06 thesis_template/0_Prelim/abs.tex
added RDD caching

\chapter{Introduction}
\label{chapter:Introduction}
\thispagestyle{myheadings}

\section{Problem Description}
\label{sec:history}

Many of popular open source cluster computing frameworks for large scale data analysis, 
such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
which require iterative process. As the amount of data increases, memory is required to keep many objects. 
Therefore, memory management plays a critical role in this task.

@@

\section{Memory Management}
\label{sec:history}

Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
but not the ownership.

>>>>

% ABSTRACT

Abstract 
Many of popular open source cluster computing frameworks for large scale data analysis, such as Hadoop and Spark, 
allow programmers to define objects in a host languages, such as Java. The objects are then managed in RAM 
by the language and its runtime, Java Virtual Machine in the case of Java and Scala. Storing objects 
in memory enables machine to process iterative computation. One of the fundamental tasks for recent big data analysis 
is analysis using Machine Learning Algorithms, which require iterative process. As the amount of data increases, memory is required to keep many objects. 
Therefore, memory management plays a critical role in this task.

@@

### 2019-10-06 thesis_template/1_Intro/intro.tex
added RDD caching

\section{Memory Management}
\label{sec:history}

@@

>>>>

\section{Memory Management in Rust}
\label{sec:history}

@@

\section{Spark and RDD Catching}
\label{sec:history}

Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
and graph analytics iteratively process the data.

In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.
